### 2022-11-15 NSF2022/Description/backgroundv3.tex
SA3
finished up background

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize (a) Granules make a
  superstructure e.g., a vesicle. The panel shows the moving domain
  $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$ with
  $|\dd_i| = 1$, and the unit inward normal $\nnu$. Panels (b), (c), (d)
  show the interplay between the phase field $\phi$ (colormap) and
  granule configuration. Red is for $\phi = 1$ and blue for $\phi = 0$;
  $W(\phi) = \tfrac{1}{2}\phi^2$. The white arrows are the fluid
  velocity field. The panels reach an equilibrium state in panel (d).}
\end{figure}

@@

To determine how the granules move through space, we look for rigid body
transformations
\begin{align}
\label{eq:RBT}
  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \oomega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
  \,\dif s = \mathbf{0},
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla \phi|^2 - \epsilon \nabla \phi \nabla \phi^T\right)
%T_i = \gamma\left[\epsilon^{-1} W(\phi)I
%  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
%  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations describing the
velocity $\uu$ and pressure $p$ of the incompressible fluid region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
of the scalar order parameter $\phi$ with a decay length $\epsilon$.
The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$, etc., representing
metastable states of the solvent. In the single-well case, $W(\phi) =
\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
equation. In the double-well case e.g, $W(\phi) =
\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
discusses certain modifications needed for~\eqref{eqn:phase} in the
nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration; $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition form bilayer configurations (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

@@

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of a continuous, permeable, inextensible,
elastic vesicle. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading
vesicle~\cite{Finken2008, Shaqfeh11} (see
Figure~\ref{fig:JPv_linearshear}). Movies of
Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip and derived
values for intermonolayer friction are in good quantitative agreement
those derived by atomistic and Martini force field simulation
studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure~\ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear
rate~\cite{VLAHOVSKA2009775, keller_skalak_1982}. A side-by-side
comparison of granule-based vesicles and the sharp interface
representation yields shapes and trajectories that basically overlapped.

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is highly desirable
from the Applied Math point of view as there are many \emph{Further
Applications}, such as (i) amphiphilic Janus spheres that form diverse
suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii) pickering
emulsions involving two-phase fluids and dense suspensions
\cite{Bradley2016}, (iii) creation and manipulation of small droplets
using amphiphilic microparticles~\cite{Ha2022SurfaceEM,
Ha2020MinimalSC}, and (iv) tension driven fabrication of
microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
Zeng20223DprintedMT, Russell2016EnergyLF}.

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[17]{r}{3.1in}
  \vspace{-8pt}
  \centering
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the partial differential equations
(PDEs)~\eqref{eqn:stokes} and~\eqref{eqn:phase} are challenging to
develop because of the complicated and unbounded domain. This challenge
is compounded when dense suspensions are considered.
Integral equations
(IEs) offer an alternative formulation of the PDEs that only require
meshing the boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and they automatically satisfy far-field
conditions. Additional advantages of discretizations of IE formulations
include high-order, or even spectral, accuracy and well-conditioned
linear system that can be solved iteratively with a mesh-independent
number of Krylov iterations such as the generalized minimal residual
method (GMRES). However, IEs have challenges: nearly touching granules
requires a quadrature rule for nearly-singular integrals; their
discretization results in dense matrices; and they cannot immediately be
applied to non-linear PDEs. \S\ref{sec:specificaim2} discusses a variety
of tools the IE community, including PI Quaife, has developed to address
these numerical challenges.

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the simulation and theory for
soft-matter systems and foster training in Mathematical Sciences.
Section~\ref{sec:BroaderImpacts} summarizes the broader impacts and
section~\ref{sec:IntellectualMerit} summarizes the intellectual merit of
our research activity. Section~\ref{sec:proposed-work} contains our
specific aims.

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize (a) The moving domain,
  $\Omega(t)$, of granules with centers $\aa_i$, directors $\dd_i$ with
  $|\dd_i| = 1$, and the unit inward normal $\nnu$. Panels (b), (c), (d)
  show the interplay between the phase field $\phi$ (colormap) and
  granule configuration. Red is for $\phi = 1$ and blue for $\phi = 0$;
  $W(\phi) = \tfrac{1}{2}\phi^2$. The white arrows are the fluid
  velocity field. The panels reach an equilibrium state in panel (d).}
\end{figure}

@@

To determine how the granules move through space, we look for rigid body
transformations
\begin{align}
\label{eq:RBT}
  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \oomega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
  \,\dif s = \mathbf{0},
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla
  \phi|^2 - \epsilon \nabla \phi \nabla \phi^T\right),
%T_i = \gamma\left[\epsilon^{-1} W(\phi)I
%  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
%  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations describing the
velocity $\uu$ and pressure $p$ of the incompressible fluid region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
of the scalar order parameter $\phi$ with a decay length $\epsilon$.
The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$, etc., representing
metastable states of the solvent. In the single-well case, $W(\phi) =
\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
equation. In the double-well case e.g, $W(\phi) =
\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
discusses certain modifications needed for~\eqref{eqn:phase} in the
nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration; $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition form bilayer configurations (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ (yellow) on the other form multilamellar
  bilayers.  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow)
  on one side and $\phi=-1$ (green) on the other side form a
  checkerboard pattern.}
\end{wrapfigure}

@@

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of a continuous, permeable, inextensible,
elastic vesicle. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading
vesicle~\cite{Finken2008, Shaqfeh11} (Figure~\ref{fig:JPv_linearshear}).
Movies of Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction are in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure~\ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear
rate~\cite{VLAHOVSKA2009775, keller_skalak_1982}. A side-by-side
comparison of granule-based vesicles and the sharp interface
representation yields shapes and trajectories that basically overlap.

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is highly desirable
from the Applied Mathematics point of view as there are many
\emph{Further Applications}, such as (i) amphiphilic Janus spheres that
form diverse suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii)
pickering emulsions involving two-phase fluids and dense suspensions
\cite{Bradley2016}, (iii) creation and manipulation of small droplets
using amphiphilic microparticles~\cite{Ha2022SurfaceEM,
Ha2020MinimalSC}, and (iv) tension driven fabrication of
microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
Zeng20223DprintedMT, Russell2016EnergyLF}.

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[17]{r}{3.1in}
  \vspace{-8pt}
  \centering
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the partial differential equations
(PDEs)~\eqref{eqn:stokes} and~\eqref{eqn:phase} are challenging to
develop because of the complicated and unbounded domain. This challenge
is compounded when dense suspensions are considered.
Integral equations
(IEs) offer an alternative formulation of the PDEs that only require
meshing the boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and they automatically satisfy far-field
conditions. Additional advantages of discretizations of IE formulations
include high-order, or even spectral, accuracy and well-conditioned
linear systems that can be solved iteratively with a mesh-independent
number of Krylov iterations such as the generalized minimal residual
method (GMRES). However, IEs have challenges: nearly touching granules
requires a quadrature rule for nearly-singular integrals, their
discretization results in dense matrices, and they cannot immediately be
applied to non-linear PDEs. \S\ref{sec:specificaim2} discusses a variety
of tools the IE community, including PI Quaife, has developed to address
these numerical challenges.

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the theory, simulation and
modeling for soft-matter systems and foster training in Mathematical
Sciences.  Section~\ref{sec:BroaderImpacts} summarizes the broader
impacts and section~\ref{sec:IntellectualMerit} summarizes the
intellectual merit of our research activity.
Section~\ref{sec:proposed-work} contains our specific aims.
